%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
 \cventry
      {Sr. Software Engineer} % Job title
      {Techona} % Organization
      {Prague, Czech Republic} % Location
      {Feb. 2017 - Present} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Casino games development using Google Closure}
          \item {UI Optimization for smartPhone, tablets and physicals slot machines}
          \item {Troubleshooting of minified code on different devices}
          \item {Build automation using NodeJS}
          \item {Prototype creation using PIXIJS, Spine and DragonBones}
        \end{cvitems}
      }

 \cventry
      {IOS Developer} % Job title
      {FreeLance IOS Developer} % Organization
      {Prague, Czech Republic} % Location
      {Nov. 2017 - Present} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Fitness app using geolocation phone capabilities}
          \item {Native IOS app on Swift 4}
        \end{cvitems}
      }

  \cventry
      {AngularJS/NodeJS Developer} % Job title
      {Devicescape} % Organization
      {San Francisco, California} % Location
      {Jul. 2016 - Feb. 2017} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {AngularJS UI development for mobile apps.}
          \item {NodeJS endpoints mockups for API testing.}
          \item {Google Analitics implementation for app tracking.}
          \item {IOS integration using Swift}
          \item {Created ProtractorJS cases for UI testing.}
          \item {Docker container for UI testing on a Jenkins Box}
          \item {NodeJS Endpoint REST API creation using BookShelfJS ORM}
        \end{cvitems}
      }


  \cventry
    {AngularJS/NodeJS Developer} % Job title
    {Bluesmart} % Organization
    {Buenos Aires, Argentina} % Location
    {Feb. 2016 - Jul. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Optimized the load times of the company website. I lowered the load times from 15 secs. to 3 secs.}
        \item {Maintained the company's e-commerce site, made with Ruby on Rails and PostgreSQL.}
        \item {Added fraud prevention fixes to the e-commerce site.}
        \item {Metric tools integration(Google Analytics, Mixpanel, Google Tag Manager, among others).}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {AngularJS Developer} % Job title
    {Inaka(an Erlang Solution Company)} % Organization
    {Buenos Aires, Argentina} % Location
    {Aug. 2015 - Feb. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Developed an administration dashboard on AngularJS, interacting a REST API made in Erlang.}
       \item {Developed E2E testings on Protractor and Celenium.}
       \item {Developed Unit Testings on Jasmine}
       \item {Developed fake REST endpoints on ExpressJS/NodeJS in order to run regression tests and day to day development}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Lead Developer} % Job title
    {The Walt Disney Company of Argentina} % Organization
    {Buenos Aires, Budapest, Uk} % Location
    {March. 2009 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Hired a team of four people in order to fulfill the needs of the region (15 countries).}
        \item {Implemented and migrated 3 different CMS's in the curse of 5+ years}
        \item {Reviewd burgets with system providers}
        \item {Followed different projects in a wide range of technologies, mostly PHP on Linux, but also Ruby on Rails and NodeJS/MongoDB}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lead Developer / Game Desinger} % Job title
    {Three Melons} % Organization
    {Buenos Aires, Argentina} % Location
    {Oct. 2007 - Feb. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created games in Flash, using ActionScript 3.0 for companies like Disney, Lego, MTV, among others.}
        \item {Led multidisciplinary teams in several projects for the named companies.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {Galicia Bank} % Organization
    {Buenos Aires, Argentina} % Location
    {Nov. 2006 - Oct. 2009} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained several colaborative systems made in Lotus Notes.}
        \item {Led a team of three people, working also with Lotus Notes among other tools.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Developer} % Job title
    {MicroGestion Software} % Organization
    {Buenos Aires, Argentina} % Location
    {Jul. 2000 - Nov. 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed colavorative systems based on the tool Lotus Notes.}
        \item {Worked as consultant in companies like Unilever, Clorox, Johnson Diversey, among others.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
