%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
 \cventry
  {C99/Webassembly Developer - Maintainer} % Job title
  {Github} % Organization
  {Prague, Czech Republic} % Location
  {Jul 2020 - Present} % Date(s)
  {
  \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created implementation of Dear IMGui for RayLib game engine}
      \item {Created starting template and examples}
      \item {https://github.com/WEREMSOFT/c99-raylib-cimgui-template}
  \end{cvitems}
  }
  \cventry
  {C99/Webassembly Developer - Maintainer} % Job title
  {Github} % Organization
  {Prague, Czech Republic} % Location
  {Jan 2020 - Present} % Date(s)
  {
  \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Created implementation of Spine Animation Library for RayLib game engine}
      \item {Created 2D and 3D versions and examples}
      \item {https://github.com/WEREMSOFT/spine-raylib-runtimes}
  \end{cvitems}
  }
  \cventry
  {C99/Webassembly Developer - Contributor} % Job title
  {FLECS} % Organization
  {Prague, Czech Republic} % Location
  {Dec 2019 - Jan 2020} % Date(s)
  {
  \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Implemented error handling on the parser}
      \item {https://github.com/SanderMertens/flecs}
  \end{cvitems}
  }

  \cventry
  {C99/Webassembly Developer} % Affiliation/role
  {Global Game Jam 2020} % Organization/group
  {Berlin} % Location
  {2020} % Date(s)
  {
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Develop Entity Component System based game in C.}
    \item {Develop game for competition.}
  \end{cvitems}
  }


  \cventry
  {C++ Programmer} % Affiliation/role
  {Global Game Jam 2019} % Organization/group
  {Prague} % Location
  {2019} % Date(s)
  {
  \begin{cvitems} % Description(s) of experience/contributions/knowledge
    \item {Develop game engine in C++.}
    \item {Develop retro game for competition.}
  \end{cvitems}
  }

  \cventry
    {Programmer/Consultor} % Affiliation/role
    {Vox Populi Vox Dei 2} % Organization/group
    {Steam - USA} % Location
    {2013 - 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Programmed the main code and visual effects.}
        \item {Designed the first bosses and level layout.}
      \end{cvitems}
    }

  \cventry
    {Programmer} % Affiliation/role
    {Naka Outdoors Mobile App} % Organization/group
    {App Store/Google Play Store} % Location
    {2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Programmed the e-commerce App on AngularJS/Phonegap.}
        \item {Published the app in the Apple App Store.}
        \item {Published the app in the Google Play Store using 2 different versions. One for older Android devices.}
      \end{cvitems}
    }
  \cventry
    {Programmer} % Affiliation/role
    {EHS App} % Organization/group
    {App Store/Google Play Store} % Location
    {2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Programmed an identity control App on AngularJS/Phonegap.}
        \item {Published the app in the Apple App Store.}
        \item {Published the app in the Google Play Store.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
